Supplementary information

### 2020-02-10 manuscript/manuscript.Rmd
alterations to site differences supplementary figure

A preliminary analysis using supervised random forest classification could separate trees based on their location (Supplementary  figure 3a) with an average *margin* value of `r site_rf_margin$Margin %>% signif(digits = 3)`.
The descriptors that contributed most to this discrimination were those that were related to trees size such as DBH, total height and crown radius and likely reflect the varied tree age and planting density across the nine sites (Supplementary figure 3b). 
To counter this, effect sizes were adjusted based on the site means for each tree size descriptor to remove inter-site variability but maintain intra-site variability as described in Section #.
This ensures that the subsequent comparisons of these descriptors in the context of oak decline are not confounded by these identified site differences.
After the application of the tree size adjustment, the random forest margin was substantially reduced to `r site_rf_post_correction_margin$Margin %>% signif(digits = 3)` indicating that the adjustment was able to remove the majority of the between site variance.

>>>>

A preliminary analysis using supervised random forest classification could separate trees based on their location (Supplementary  figure 3a) with an average *margin* value of `r site_rf_margin$Margin %>% signif(digits = 3)`.
The descriptors that contributed most to this discrimination were those that were related to trees size such as DBH, total height and crown radius and likely reflect the varied tree age and planting density across the nine sites (Supplementary figure 3b). 
To counter this, effect sizes were adjusted based on the site means for each tree size descriptor to remove inter-site variability but maintain intra-site variability as described in Section #.
This ensures that the subsequent comparisons of these descriptors in the context of oak decline are not confounded by these identified site differences.
After the application of the tree size adjustment, the average random forest margin value was substantially reduced to `r site_rf_post_correction_margin$Margin %>% signif(digits = 3)`.
This negative value indicates that the adjustment was able to remove the majority of the between site variance and that the random forest models were on average unable to correctly classify the site locations of the trees.

### 2020-02-10 manuscript/supplementary.Rmd
alterations to site differences supplementary figure

```{r site_differences,fig.cap='Differences between sites in phenotypic descriptors analysed by supervised Random Forest. a) Multidimensional scaling (MDS) plot of random forest proximity values of individual trees scaled to two dimensions. Mean margin value shown. b) Descriptor importances measures.',fig.height=6}
loadd(site_differences_mds_plot)
grid.arrange(site_differences_mds_plot$a,site_differences_mds_plot$b,nrow = 1)
```

>>>>

```{r site_differences,fig.cap='Differences between sites in phenotypic descriptors analysed by supervised random forest classification. a) Multidimensional scaling (MDS) scatter plot of random forest proximity values of individual trees scaled to two dimensions. b) Descriptor mean decrease in accuracy importances measures. Descriptors ordered in descending importance.',fig.height=6}
loadd(site_differences_mds_plot)
grid.arrange(site_differences_mds_plot$a,site_differences_mds_plot$b,nrow = 1)
```
